### 2011-12-02 docs/src/manual.tex

\item[\fbox{\code{+/-ghci}}]
Turn on/off the ghci mode.
In the ghci mode, the initial goal is send to the interactive version
of the Glasgow Haskell Compiler. This might result in a slower
execution but in a faster startup time since the linker
to create the main executable is not used.

\item[\fbox{\code{copts $o$}}]\pindex{copts}
Define additional options passed to the KiCS2 compiler.
For instance, setting the option
\begin{curry}
:set copts -O 0
\end{curry}
has the effect that all optimizations performed by the KiCS2 compiler
are turned off.

\item[\fbox{\code{rts $o$}}]\pindex{rts}
Define additional run-time options passed to the executable
generated by the Glasgow Haskell Compiler, i.e., the parameters
\ccode{+RTS $o$ -RTS} are passed to the executable.
For instance, setting the option
\begin{curry}
:set rts -H512m
\end{curry}
has the effect that the minimum heap size is set to 512 megabytes.

>>>>

\item[\fbox{\code{+/-ghci}}]\pindex{ghci}
Turn on/off the ghci mode.
In the ghci mode, the initial goal is send to the interactive version
of the Glasgow Haskell Compiler. This might result in a slower
execution but in a faster startup time since the linker
to create the main executable is not used.

\item[\fbox{\code{cmp $opts$}}]\pindex{cmp}
Define additional options passed to the KiCS2 compiler.
For instance, setting the option
\begin{curry}
:set cmp -O 0
\end{curry}
has the effect that all optimizations performed by the KiCS2 compiler
are turned off.

\item[\fbox{\code{ghc $opts$}}]\pindex{ghc}
Define additional options passed to the Glasgow Haskell Compiler
when the generated Haskell programs are compiled.
Usually, such options are useful only for experimental purposes.
For instance, setting the option
\begin{curry}
:set ghc -DDISABLE_CS
\end{curry}
has the effect that the constraint store used to enable
an efficient access to complex bindings is disabled.
Similarly,
\begin{curry}
:set ghc -DSTRICT_VAL_BIND
\end{curry}
has the effect that expressions in a unification constraint
(\code{=:=}) are always fully evaluated
(instead of the evaluation to a head normal form only)
before unifying both sides.
Since these options influence the compilation of the run-time system,
one should also enforce the recompilation of Haskell programs
by the GHC option \ccode{-fforce-recomp}, e.g., one should set
\begin{curry}
:set ghc -DDISABLE_CS -fforce-recomp
\end{curry}

\item[\fbox{\code{rts $opts$}}]\pindex{rts}
Define additional run-time options passed to the executable
generated by the Glasgow Haskell Compiler, i.e., the parameters
\ccode{+RTS $o$ -RTS} are passed to the executable.
For instance, setting the option
\begin{curry}
:set rts -H512m
\end{curry}
has the effect that the minimum heap size is set to 512 megabytes.

\item[\fbox{\code{args $arguments$}}]\pindex{args}
Define run-time arguments passed to the executable
generated by the Glasgow Haskell Compiler.
For instance, setting the option
\begin{curry}
:set args first second
\end{curry}
has the effect that the I/O operation \code{getArgs}
(see library \code{System} (Section~\ref{Library:System})
returns the value \code{["first","second"]}.
